\chapterstyle{biosketch}
\setsecnumformat{\csname the#1\endcsname.\space}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand{\thesubsection}{\roman{subsection}}

\chapter{Geoffrey Challen}

Geoffrey Challen (n\'{e} Werner-Allen)\\
Department of Computer Science and Engineering\\
University at Buffalo\\
338 Davis Hall\\
Buffalo, NY 14260-2500\\
\href{mailto:challen@buffalo.edu}{\texttt{challen@buffalo.edu}}\\
\url{http://www.cse.buffalo.edu/~challen/}

\section{Professional Preparation}

\begin{itemize}
\item Harvard University, Physics, A.B. 2003
\item Harvard University, Computer Science, Ph.D. 2010
\item Massachusetts Institute of Technology, Post-Doctoral Researcher, 2010-2011
\end{itemize}

\section{Appointments}

Assistant Professor, University at Buffalo, 07/15/2011--present.

\section{Products}

\subsection{Related Products}

\begin{enumerate}

\item \textbf{The Case for Power-Agile Computing}\\\uline{Geoffrey Challen}
and Mark Hempstead. In \emph{Proceedings of the 13th Workshop of Hot Topics
in Operating Systems (HotOS'11)}, May, 2011.
\nocite{poweragile-hotos11}

\item \textbf{IDEA: Integrated Distributed Energy Awareness for Wireless Sensor
Networks}\\ \uline{Geoffrey Werner Challen}, Jason Waterman and Matt Welsh. In
\emph{Proceedings of the 8th Annual International Conference on Mobile Systems,
Applications and Services (MobiSys'10)}, June, 2010.
\nocite{idea-mobisys10}

\item \textbf{Lance: Optimizing High-Resolution Data Collection in Wireless
Sensor Networks}\\ \uline{Geoffrey Werner-Allen}, Stephen Dawson-Haggerty and
Matt Welsh. In \emph{Proceedings of the Sixth ACM Conference on Embedded
Networked Sensor Systems (SenSys'08)}, November, 2008.
\nocite{lance-sensys08}

\item \textbf{PhoneLab: A Programmable Smartphone Testbed} (Invited Paper)\\
Anandatirtha Nandugudi, Anudipa Maiti, Taeyeon Ki, Fatih Bulut, Murat
Demirbas, Tevfik Kosar, Chunming Qiao, Steven Y. Ko and \uline{Geoffrey
Challen}. To appear in \emph{Proceedings of the First International Workshop
on Sensing and Big Data Mining (SenseMine'13)}, November, 2013.\\
\href{http://www.phone-lab.org}{\texttt{http://www.phone-lab.org}}. Online
public testbed. \nocite{phonelab-url,phonelab-sensemine13}

\item \textbf{\texttt{ops-class.org}: Operating Systems Education Online}\\
\href{http://www.ops-class.org}{\texttt{http://www.ops-class.org}}. Online
operating systems classroom supporting courses using the OS~161 educational
operating system.
\nocite{opsclass-url}

\end{enumerate}

\subsection{Significant Products}

\begin{enumerate}

\item \textbf{Mercury: A Wearable Sensor Network Platform for High-Fidelity
Motion Analysis}\\ Konrad Lorincz, Bor-rong Chen, \uline{Geoffrey Werner
Challen}, Atanu Roy Chowdhury, Shyamal Patel, Paolo Bonato and Matt Welsh. In
\emph{Proceedings of the Seventh ACM Conference on Embedded Networked Sensor
Systems (SenSys'09)}, November, 2009.
\nocite{mercury-sensys09}

\item \textbf{Peloton: Coordinated Resource Management for Sensor Networks}\\
Jason Waterman, \uline{Geoffrey Werner Challen}, and Matt Welsh. In
\emph{Proceedings of the 12th Workshop on Hot Topics in Operating Systems
(HotOS'09)}, May, 2009.
\nocite{peloton-hotos09}

\item \textbf{Resource Aware Programming in the Pixie OS}\\ Konrad Lorincz,
Bor-rong Chen, Jason Waterman, \uline{Geoff Werner-Allen} and Matt Welsh. In
\emph{Proceedings of the Sixth ACM Conference on Embedded Networked Sensor
Systems (SenSys'08)}, November, 2008.
\nocite{pixie-sensys08}

\item \textbf{Fidelity and Yield in a Volcano Monitoring Sensor Network}\\
\uline{Geoffrey Werner-Allen}, Konrad Lorincz, Jeff Johnson, Jonathan Lees and
Matt Welsh. In \emph{Proceedings of the Seventh USENIX Symposium on Operating
Systems Design and Implementation (OSDI'06)}, November, 2006.
\nocite{volcano-osdi06}

\item \textbf{Firefly-Inspired Sensor Network Synchronicity with Realistic
Radio Effects}\\ \uline{Geoffrey Werner-Allen}, Geetika Tewari, Ankit Patel,
Radhika Nagpal and Matt Welsh. In \emph{Proceedings of the Third ACM
Conference on Embedded Networked Sensor Systems (SenSys'05)}, November, 2005.
\nocite{firefly-sensys05}

\end{enumerate}

\section{Synergistic Activities}

\begin{itemize}

\item Program committee member: 11th ACM Conference on Embedded Networked
Sensor Systems (SenSys'13), Program committee member: 10th ACM Conference on
Embedded Networked Sensor Systems (SenSys'12), 9th ACM Conference on Embedded
Networked Sensor Systems (SenSys'11), 31st IEEE Real-Time Systems Symposium
(RTSS 2011) (Wireless Network Systems Track).

\item 2009-2010 Siebel Scholar.

\end{itemize}

\section{Collaborators \& Other Affiliations}

\subsection{Collaborators and Co-Editors}

Murat Demirbas (University at Buffalo), Mark Hempstead (Drexel University),
Branislav Kusy (CSIRO), Steven Y. Ko, Tevfik Kosar, Chunming Qiao (University
at Buffalo).

\subsection{Graduate Advisers and Postdoctoral Sponsors}

Matt Welsh (Google), Hari Balakrishnan (Massachusetts Institute of Technology).

\subsection{Thesis Adviser and Postgraduate-Scholar Sponsor}

Anand Nandugudi, Anudipa Maiti, Taeyeon Ki, Guru Prasad, Jinghao Shi
(University at Buffalo).

Total number of graduate students advised: 5; postgraduate-scholars
sponsored: 0.

% 16 Nov 2010 : GWA : All pubs follow.

%\item \textbf{Mercury: A Wearable Sensor Network Platform for High-Fidelity
%Motion Analysis}\\ Konrad Lorincz, Bor-rong Chen, \uline{Geoffrey Werner
%Challen}, Atanu Roy Chowdhury, Shyamal Patel, Paolo Bonato and Matt Welsh. In
%\emph{Proceedings of the Seventh ACM Conference on Embedded Networked Sensor
%Systems (SenSys’09)}, November, 2009.
%\nocite{mercury-sensys09}
%
%\item \textbf{Peloton: Coordinated Resource Management for Sensor Networks}\\
%Jason Waterman, \uline{Geoffrey Werner Challen}, and Matt Welsh. In
%\emph{Proceedings of the 12th Workshop on Hot Topics in Operating Systems
%(HotOS-XII)}, May, 2009.
%\nocite{peloton-hotos09}
%
%\item \textbf{Resource Aware Programming in the Pixie OS}\\ Konrad Lorincz,
%Bor-rong Chen, Jason Waterman, \uline{Geoff Werner-Allen} and Matt Welsh. In
%\emph{Proceedings of the Sixth ACM Conference on Embedded Networked Sensor
%Systems (SenSys’08)}, November, 2008.
%\nocite{pixie-sensys08}
%
%\item \textbf{Pixie: An Operating System for Resource-Aware Programming of
%Embedded Sensors}\\ Konrad Lorincz, Bor-rong Chen, Jason Waterman,
%\uline{Geoffrey Werner-Allen}, and Matt Welsh. In \emph{Proceedings of the
%Fifth Workshop on Embedded Networked Sensors (HotEmNets’08)}, June, 2008.
%\nocite{pixie-hotemnets08}
%
%\item \textbf{Fidelity and Yield in a Volcano Monitoring Sensor Network}\\
%\uline{Geoffrey Werner-Allen}, Konrad Lorincz, Jeff Johnson, Jonathan Lees and
%Matt Welsh. In \emph{Proceedings of the Seventh USENIX Symposium on Operating
%Systems Design and Implementation (OSDI’06)}, November, 2006.
%\nocite{volcano-osdi06}
%
%\item \textbf{Simulating the Power Consumption of Large-Scale Sensor Network
%Applications}\\ Victor Shnayder, Mark Hempstead, Bor-rong Chen, \uline{Geoff
%Werner-Allen} and Matt Welsh. In \emph{Proceedings of the Second ACM Conference
%on Embedded Networked Sensor Systems (SenSys’04)}, November, 2004.
%\nocite{powertossim-sensys04,

%\item \textbf{Firefly-Inspired Sensor Network Synchronicity with Realistic
%Radio Effects}\\ \uline{Geoffrey Werner-Allen}, Geetika Tewari, Ankit Patel,
%Radhika Nagpal and Matt Welsh. In \emph{Proceedings of the Third ACM Conference
%on Embedded Networked Sensor Systems (SenSys'05)}, November, 2005.
%\nocite{firefly-sensys05}
%
%\item \textbf{MoteLab: A Wireless Sensor Network Testbed}\\ \uline{Geoffrey
%Werner-Allen}, Pat Swieskowski, and Matt Welsh. In \emph{Proceedings of the
%Fourth International Conference on Information Processing in Sensor Networks
%(IPSN'05)}, April, 2005.
%\nocite{motelab-ipsn05}
%
%\item \textbf{Monitoring Volcanic Eruptions with a Wireless Sensor Network}\\
%\uline{Geoffrey Werner-Allen}, Jeff Johnson, Mario Ruiz, Jonathan Lees, and
%Matt Welsh. In \emph{Proceedings of the Second European Workshop on Wireless
%Sensor Networks (EWSN'05)}, January, 2005.
%\nocite{volcano-ewsn05}
